cardinalR: Generating interesting high-dimensional data structures

### 2025-09-16 paper-cardinalR.Rmd
Updated cube description with normalise text

The first is the regular grid of points of $n$ points in $p$ dimensions. This is generated using `gen_gridcube(n, p)`. The number of grid points along each axis is determined by finding the nearest integer factors whose product is close to $n$. In the base cube function, the cube is represented in integer grid coordinates (e.g. 1, 2, 3, ...) along each ais. This results in a $p\text{-}D$ hyercube-shaped lattice structure.

>>>>

The first is the regular grid of points of $n$ points in $p$ dimensions. This is generated using `gen_gridcube(n, p)`. The number of grid points along each axis is determined by finding the nearest integer factors whose product is close to $n$. Each dimension is then normalized to lie in the interval $[0,1]$, so that the resulting structure forms a true $p\text{-}D$ hypercube. This produces a lattice of evenly spaced points along all axes, providing a uniform and interpretable high-dimensional grid.

### 2025-09-16 paper-cardinalR.tex
Updated cube description with normalise text

The first is the regular grid of points of \(n\) points in \(p\) dimensions. This is generated using \texttt{gen\_gridcube(n,\ p)}. The number of grid points along each axis is determined by finding the nearest integer factors whose product is close to \(n\). In the base cube function, the cube is represented in integer grid coordinates (e.g.~1, 2, 3, \ldots) along each ais. This results in a \(p\text{-}D\) hyercube-shaped lattice structure.

>>>>

The first is the regular grid of points of \(n\) points in \(p\) dimensions. This is generated using \texttt{gen\_gridcube(n,\ p)}. The number of grid points along each axis is determined by finding the nearest integer factors whose product is close to \(n\). Each dimension is then normalized to lie in the interval \([0,1]\), so that the resulting structure forms a true \(p\text{-}D\) hypercube. This produces a lattice of evenly spaced points along all axes, providing a uniform and interpretable high-dimensional grid.
